Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2015-11-20 ijar-npb-ms.tex
some corrections for pmf and discrete hazard
renaming the pmf to f
prior-data conflict illustration example
figure for pdc example in sec 4 ready

The set of functioning probabilities $\{ p^k_t, t \in {\cal T}\}$
defines a discrete failure time distribution for components of type $k$ through
\begin{align*}
R^k(t_j) &= p^k_{t_j},\ t \in {\cal T} = \{t_1, \ldots, \tmax\}\,.
\end{align*}
We can express this failure time distribution also through the probability mass function (pmf) and the discrete hazard function,
\begin{align*}
q_k(t_j) &= P(T^k = t_j) = p^k_{t_j} - p^k_{t_{j+1}}\,,\\ 
h_k(t_j) &= P(T^k = t_j \mid T^k \ge t_j) = \frac{q_k(t_j)}{R(t_j)}\,.
\end{align*}
We assume the time grid $\cal T$ is dense enough for the application at hand,
otherwise it would be possible to assume, e.g.,
$R^k(t) = p^k_{t_j}, t \in [t_j, t_{j+1})$,
or taking $p^k_{t_j}$ and $p^k_{t_{j+1}}$ as upper and lower bounds for $R^k(t)$, $t \in [t_j, t_{j+1})$.

@@

>>>>

The set of functioning probabilities $\{ p^k_t, t \in {\cal T}\}$
defines a discrete failure time distribution for components of type $k$ through
\begin{align*}
R^k(t_j) &= P(T^k > t_j) = p^k_{t_j},\ t_j = t_1, \ldots, \tmax\,.
\end{align*}
We can express this failure time distribution also through the probability mass function (pmf) and the discrete hazard function,
\begin{align*}
f^k(t_j) &= P\big(T^k \in (t_j,t_{j+1}]\big) = p^k_{t_j} - p^k_{t_{j+1}}\,,\\ 
h^k(t_j) &= P\big(T^k \in (t_j,t_{j+1}]\mid T^k > t_j\big) = \frac{f^k(t_j)}{R^k(t_j)}\,. % or R^k(t_{j-1}) ???
\end{align*}
We assume the time grid $\cal T$ is dense enough for the application at hand,
otherwise it would be possible to assume, e.g.,
$R^k(t) = p^k_{t_j}, t \in [t_j, t_{j+1})$,
or taking $p^k_{t_j}$ and $p^k_{t_{j+1}}$ as upper and lower bounds for $R^k(t)$, $t \in [t_j, t_{j+1})$.

@@

As a simple example, see Figure~\ref{fig:singleprior-pdc} ***

\begin{figure}
\includegraphics[width=\textwidth]{singleprior-pdc}
\caption{Beta densities (left) and corresponding Beta-binomial probability mass functions (right)
for a prior with $\nktz = 8, \yktz = 0.75$,
and posteriors based on $n^k_t=16$ observations with $s^k_t=12$ (Posterior 1) and $s^k_t=0$ (Posterior 2), respectively.
For Posterior 2, the conflict between prior assumptions and data is averaged out;
both posterior density and posterior predictive have the same spread as Posterior 1 for which there is no conflict,
giving a false sense of certainty.}
\label{fig:singleprior-pdc}
\end{figure}
